\begin{abstract}

% %
% MOTIVATION
% %
As computing is getting more ubiquitous in our lives, computer infrastructures are getting increasingly complex and software applications are required to meet high level performance.

%
% %
% PROBLEM STATEMENT
% %
In this context, knowing how to design and optimize computer systems and networks is one of the most important skills for software engineers and a strategic asset for companies, both in terms of technology and investments.

% %
% APPROACH
% %
In this technical report we propose a next-event simulator to analyze the performance of a two-layers Fog-like system that serves classed workloads and leverages an off-loading policy between its layers.
%
First, we describe how we implemented the multi-stream pseudo-random number generator, that is the fundamental building block to provide any next-event simulator with random components.
%
Then, we describe the performance model in terms of (i) goals, (ii) conceptual model, (iii) specification model, (iv) computational model, (v) verification and (vi) validation.
%
At the end, we evaluate (i) the system performance, both analytically and experimentally computed, and (ii) the quality of the adopted pseudo-random number generator.
%
% %
% RESULTS
% %
The experimental results show (i) the satisfactory randomness degree of the adopted pseudo-random number generator and (ii) the effectiveness of our model to study the system so as to, for example, tune it in order to achieve better performance.
%
% %
% CONCLUSIONS
% %
Furthermore, we conclude our work delineating possible improvements for our simulator.

\end{abstract}
