\section{Semidecidability of the CF Regularity Problem}
\label{sec:semidecidability}

We know that the context-free regularity problem is undecidable
\cite{Pettorossi13}, due to its reduction to the undecidable Post Correspondence
Problem \cite{Hopcroft06}.

We prove the semidecidability and the undecidability of the context-free
regularity problem.

\begin{theorem}
	\label{thm:semidecidability-mnf}
	Given a context-free grammar, the problem of saying whether or not there
	exists an equivalent grammar in Marciani Normal Form is semidecidable and
	undecidable.

	\begin{proof}
		Let us consider a context-free grammar in Chomsky Normal Form.
		Let us derive an equivalent grammar by unfolding every production,
		until getting the productions for the axiom only.
		Now, it' easy to check if the derived grammar is in Marciani Normal Form.
		So, given any context-free grammar in Chomsky Normal Form, it is always
		possible to check if there exists an equivalent context-free grammar in
		Marciani Normal Form.

		As this possibility holds for grammars in Chomsky Normal Form, then it
		holds for every context-free grammar \cite{Pettorossi13}.
	\end{proof}
\end{theorem}

\begin{theorem}
	\label{thm:semidecidability}
	The context-free regularity problem is semidecidable and undecidable.

	\begin{proof}
		Follows from the semidecidability and undecidability of the problem of
		saying whether or not, given a context-free grammar, there exists an
		equivalent grammar in Marciani Normal Form, and from the regularity of
		the language generated by a context-free grammar in Marciani Normal Form.
	\end{proof}
\end{theorem}
